Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-13 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}
\label{sec:Gleason}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}

\label{sec:Gleason}

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain QIVPMs, we also want to understand what
a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
This result will first be generalized, and then we will show some
QIVPMs may not be induced by any classical IVPM, i.e., no state is
consistent with these kind of QIVPMs.

The quantum probability measure~$\mu_{1}$ maps some projectors to
$0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
to get $\bar{\mu}_{3}$. This is replacing two numbers by the smallest
intervals containing them. In general, any set of the numbers can
be replaced by the interval containing them if we carefully pick a
set of overlapping intervals. For example, consider the following
collection of intervals: 
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\{\imposs,\necess\}
\end{eqnarray}
which are overlapping intervals with length~$1/n$ except the intervals
at length~$\left(2n\right)^{-1}$ at each end. Then, any Born rule
probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional Hilbert
space can induce a QIVPM over the intervals above as follows. We first
define a map $\widehat{\iota}_{n}$ from $[0,1]$ to $\widehat{\mathscr{I}}_{n}$
as: 
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$; 
\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by one of the following: 
\begin{enumerate}
\item $k$ even and $\frac{k-0.5}{2n}\le x\le\frac{k+0.5}{2n}$; 
\item $k$ odd and $\frac{k-0.5}{2n}<x<\frac{k+0.5}{2n}$. 
\end{enumerate}
\end{itemize}
It is now not difficult to verify that $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM. For example, consider $n=2$, 
\begin{eqnarray}
\widehat{\mathscr{I}}_{1} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\nonumber \\
 &  & \cup\{\imposs,\necess\}\nonumber \\
 & = & \left\{ \imposs,\left[0,\frac{1}{4}\right],\left[0,\frac{1}{2}\right],\left[\frac{1}{4},\frac{3}{4}\right],\right.\nonumber \\
 &  & \left.\left[\frac{1}{2},1\right],\left[\frac{1}{4},1\right],\necess\right\} \,.
\end{eqnarray}
Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
can be computed by Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
from $\mu_{1}$}
\end{table}

\yutsung{Clean up until here.}
